Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-03 paper.tex
Comments on reproducibility intro

             Containeri
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        Reproducibility is a vital component to all scientific workflows. 
        Without reproducibility, correctness of results could never be 
        determined. Reproducibility is defined as the ability to obtain similar 
        results by 
        recreating or executing the original workflow on the same or different
        infrastructure\note{cite}. It have been found that more than 70\% of
        scientific experiments are not reproducible \note{cite Mbaker}

        Current studies show that different tools 
        performing the same function, in addition to the same versions of tools 
        executing on top of different operating systems produce significantly 
        dissimilar results. As a result, it is necessary that specific details 
        on the workflow, such a data used, software versions and operating 
        system used are provided. For this reason, many workflow engines have
        incorporated provenance tracking into their design.

@@

        This chapter will examine how different workflow engines tackle the 
        issue of reproducibility. Section~\ref{prov} will discuss how the 
        engines assimilate and distribute the provenance data. 
        Section~\ref{repcont} will examine how these engines use containers to
        facilitate reproducibility of the experiments.
        \section{Provenance Tracking}\label{prov}

>>>>

             Containeri
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        Reproducibility is a vital \tristan{critical?} component to all scientific workflows. 
        Without reproducibility, correctness of results could never be 
        determined. Reproducibility is defined as the ability to obtain similar 
        results by 
        recreating or executing the original workflow on the same or different
        infrastructure\note{cite Peng 2011}. It has been found that more than 70\% of
        scientific experiments are not reproducible \note{cite Mbaker}

        Current studies show that different tools 
        performing the same function, in addition to the same versions of tools 
        executing on top of different operating systems, produce significantly 
        dissimilar results \cite{bowring, gronenschild 2011, glatard 2015}. As a result, it is necessary that specific details 
        on the workflow, such a data used, software versions and operating 
        system used are provided. For this reason, many workflow engines have
        incorporated provenance tracking into their design.

@@

        This chapter will examine how different workflow engines tackle the 
        issue of reproducibility. Section~\ref{prov} will discuss how the 
        engines assimilate and distribute the provenance data. 
        Section~\ref{repcont} will examine how these engines use containers to
        facilitate reproducibility of the experiments.
        \section{Provenance Tracking}\label{prov}
            Provenance tracking is \weird{of vital importance} \tristan{twice} to scientific reporting.
            On its own, source code is insufficient to reproduce the workflow 
            described in a research paper. This is because source code does 
            not specify the specific dataset used nor the specific versions of
            tools and the environments that they were executed on. Minor 
            changes to any of these features can significantly affect results.

            As explained by the W3 PROV specification, provenance details 
            information on the data, the tools involved in its creation, and the
            responsible parties. Provenance tracking, in the context of 
            workflows, is the act of capturing provenance data during
            workflow execution. With detailed provenance and access to source 
            code information, researchers should have enough information to be able 
            to reproduce workflows.

            To to the importance of provenance tracking for scientific 
            workflows several workflow engines adapted strategies to capture 
            comprehensive provenance data. These include Nipype, PSOM, FastR, 
            LONI, Taverna, Pegasus, Nextflow, Galaxy. Other workflow engines,
            such as SPM, AA, Pydpiper,
